Lasso_RCI_Response

### 2024-02-20 Lasso_RCI_Response.Rmd
FP has identity issues

# Left join the FDR adjusted p.value
FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
FP.min.dep
```
1se -
```{r}

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep
```

@@

  tidy.summary.min.anx <- tidy(glm_min_anx)
  tidy.summary.min.anx
# Coefficients
  coefs.min.anx <- abs(coef(glm_min_anx))

# Odds ratio
  OR.min.anx <- exp(coef(glm_min_anx))

# OR 95% CI
  CI.min.anx <- data.frame(exp(confint(glm_min_anx)))

# P values
  p.values.min.anx <- data.frame(cbind(tidy.summary.min.anx$term,tidy.summary.min.anx$p.value))
  # FDR Adjusted P Values
    adj.p.min.anx <- FDR(pvalues = p.values.min.anx)
    ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))

# R^2 values  
   R2.min.anx <- performance::r2(glm_min_anx)

@@

# Left join the FDR adjusted p.value
FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
FP.min.anx
```
1se -
```{r}

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx
```

>>>>

# Left join the FDR adjusted p.value
FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
FP.min.dep$type = c("Depression")
FP.min.dep
```
1se -
```{r}

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep$type = c("Depression")
FP.1se.dep
```

@@

  tidy.summary.min.anx <- tidy(glm_min_anx)
  tidy.summary.min.anx
# Coefficients
  coefs.min.anx <- round(abs(coef(glm_min_anx)),3)

# Odds ratio
  OR.min.anx <- round(exp(coef(glm_min_anx)),3)
# OR 95% CI
  CI.min.anx <- data.frame(exp(confint(glm_min_anx)))
  CI.min.anx[,1] = round(CI.min.anx[,1],3)
  CI.min.anx[,2] = round(CI.min.anx[,2],3)
# P values
  p.values.min.anx <- data.frame(cbind(tidy.summary.min.anx$term,tidy.summary.min.anx$p.value))
  # FDR Adjusted P Values
    adj.p.min.anx <- FDR(pvalues = p.values.min.anx)
    ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))
    ADJ.p.values.min.anx
# R^2 values  
   R2.min.anx <- performance::r2(glm_min_anx)

@@

# Left join the FDR adjusted p.value
FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
FP.min.anx$p.values = round(as.numeric(FP.min.anx$p.values),3)
FP.min.anx$p.adjusted = round(as.numeric(FP.min.anx$p.adjusted),3)
FP.min.anx$type = c("Anxiety")
FP.min.anx

```
1se -
```{r}

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx$type = c("Anxiety")
```

# Forrest Plot

```{r}
#Create order varaible in dataset to keep it the same as the regression
FP.min.anx$order = c(rev(seq(length(FP.min.anx$Variable),1)))
FP.min.anx

```{r}
FP.min.anx |>
  ggplot(aes(y = reorder(Variable, -order))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape=10, size=2.5,show.legend = FALSE) +
    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5)+
  #change x axis name
  labs(
    x="Odds Ratio",
    # title = "Odds of Reporting Medical Conditions",
    # subtitle = "Based Upon Probable TBI/concussion") +
       ) 
  #adjust the dimentions. 
  #coord_cartesian(ylim = c(1,length(FP.min.anx$Variable))) +
  #add a line at 0 for reference

  #add anotations to help suggests what each side means.
  # annotate("text", x = .5, y = 14, label = "Less Likely", size= 3) +
  # annotate("text", x = 1.5, y = 14, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())
